---
output: 
  html_document:
    self_contained: false

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

dt_options = list(dom          = '<"pull-right" B> frtip',  
                  ordering     = T, 
                  lengthChange = F, 
                  pageLength   = 20,
                  buttons      = list(list(extend = 'csv',
                                           text = "Download Excel/CSV",
                                           title = "Air toxicity values",
                                           filename = 'MPCA air toxicity values.csv'), 
                                      list(extend = 'pdf',
                                           text = "PDF",
                                           title = "Air toxicity values",
                                           pageSize = 'A4',
                                           orientation = 'landscape',
                                           filename = 'MPCA air toxicity values.pdf'), 
                                      list(extend = 'print',
                                           text = "Print",
                                            title = "Air toxicity values")
                  ))

```


<style>
  .blue {background-color: #e6f0ff; border-radius: 5px; padding: 20px;}
  body {margin-left: 0px;}
  p {font-size: 17px;}
  .dataTables_filter {margin-right: 12px;}
  .dt-buttons a {margin-left: 8px; background-color: #e6f0ff; margin-top: -3px;} 
  .pull-right {float: right; margin-top: 0;}
  th {font-size 12px;}
  h2 {margin-top: 22px;}
  h3 {margin-top: 22px; margin-bottom: 22px;}
</style>


## Ambient air toxicity values used by MPCA
### Values in units of _ug/m3_


```{r rass, echo = F, warning = F, message = F}
#An Excel table of the values may be found in the `ToxValues` tab of the [Risk Assessment Spreadsheet]( https://www.pca.state.mn.us/air/aera-risk-screening-rass-and-qchi).

library(readxl)
library(knitr)
library(kableExtra)
library(dplyr)
library(DT)

rass <- read_excel("X:/Agency_Files/Outcomes/Risk_Eval_Air_Mod/_Air_Risk_Evaluation/AERA program/RASS/AERA RASS (aq9-22-7) 2019-02.xlsx", "Tox Values", skip = 19, n_max = 372, col_names = T)

rass <- rass %>%
  select(`CAS # or MPCA#`, `Chemical Name`, `Tox Value Source..6`, `Acute Air Conc. (ug/m3)`, `Tox Value Source..13`, `10-5 Cancer-based Air Conc (ug/m3)`, `Tox Value Source..19`, `Reference Conc. (ug/m3)..20`) %>%
  rename(CAS = `CAS # or MPCA#`, 
        `Acute Air Concentration` = `Acute Air Conc. (ug/m3)`,
        `Acute Air Concentration Source` = `Tox Value Source..6`,
         `Cancer Based Air Concentration` = `10-5 Cancer-based Air Conc (ug/m3)`,
         `Cancer Based Air Concentration Source` = `Tox Value Source..13`,
         `Non-Cancer Chronic Air Concentration` = `Reference Conc. (ug/m3)..20`,
         `Non-Cancer Chronic Air Concentration Source` = `Tox Value Source..19`) %>%
  mutate(`Acute Air Concentration` = round(as.numeric(`Acute Air Concentration`), digits = 2),
         `Cancer Based Air Concentration` = round(as.numeric(`Cancer Based Air Concentration`), digits = 2),
         `Non-Cancer Chronic Air Concentration` = round(as.numeric(`Non-Cancer Chronic Air Concentration`), digits = 2)) %>%
  filter(!is.na(CAS)) 

rass <- rass %>%
  mutate(`Acute Air Concentration` = ifelse(is.na(`Acute Air Concentration`), " ", `Acute Air Concentration`),
         `Cancer Based Air Concentration` = ifelse(is.na(`Cancer Based Air Concentration`), " ", `Cancer Based Air Concentration`),
        `Non-Cancer Chronic Air Concentration` =  ifelse(is.na(`Non-Cancer Chronic Air Concentration`), " ", `Non-Cancer Chronic Air Concentration`),
        `Acute Air Concentration Source` = ifelse(is.na(`Acute Air Concentration Source`), " ", `Acute Air Concentration Source`),
         `Cancer Based Air Concentration Source` = ifelse(is.na(`Cancer Based Air Concentration Source`), " ", `Cancer Based Air Concentration Source`),
        `Non-Cancer Chronic Air Concentration Source` =  ifelse(is.na(`Non-Cancer Chronic Air Concentration Source`), " ", `Non-Cancer Chronic Air Concentration Source`))
                                            
DT::datatable(rass, 
              rownames   = F,
              extensions = "Buttons",
              options    = dt_options) %>% 
    formatStyle(columns = 1:ncol(rass), fontSize = '90%')
                 

```

<br>

<div class = "blue">

## Toxicity Value Source Information
</div>

```{r acronym table, echo = F, message = F}
names <- c("Acronym", "Source Name", "URL link")
hbvs <- c("HBV or RAA", "MDH Health Based Value or Risk Assessment Advice", "www.health.state.mn.us/communities/environment/risk/guidance/air/table.html")
hrvs <- c("HRV", "MDH Health Risk Value", "www.health.state.mn.us/communities/environment/risk/guidance/air/table.html")
calepa <- c("Cal EPA", "California Environmental Protection Agency Office of Environmental Health Hazard", "http://oehha.ca.gov/air/hot_spots/")
iris <- c("IRIS", "USEPA Integrated Risk Information System", "http://www.epa.gov/IRIS/")
pprtv <- c("PPRTV", "EPA Provisional Peer Reviewed Toxicity Values for Superfund", "http://hhpprtv.ornl.gov/")

acronym_table <- rbind(names, hbvs, hrvs, iris, calepa, pprtv)
acronym_table <- data.frame(acronym_table, row.names = NULL)
colnames(acronym_table) = as.character(unlist(acronym_table[1, ])) # the first row will be the header
acronym_table = acronym_table[-1, ]  
acronym_table <- data.frame(acronym_table, row.names = NULL, check.names = FALSE)

#print(datatable(acronym_table, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX = T)))
kable(acronym_table) %>%
 kable_styling(bootstrap_options = c("striped", "hover"))
```

